Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-21 sections/eval.tex
Update on Overleaf.

\begin{table}[htbp]
    \centering
    \caption{SpMV Tensor Formats}
    \begin{tabular}{|l|l|l|l|l|}
        \hline
        \textbf{Tensor Format} & \textbf{Style of Matrix} & \textbf{Evaluation Datasets} \\
        \hline
        SparseList & sparse matrices & Vuduc, Ahrens, TACO, SNAP, synthetic \\
        \hline
        SparseVBL & matrices with a clear blocked structure & Vuduc, Ahrens, TACO, SNAP, synthetic  \\
        \hline 
        SparseBand & matrices with a diagonal band & Vuduc, Ahrens, TACO, SNAP, synthetic \\ 
        \hline 
        SparsePoint & matrices with one value per row & synthetic \\
        \hline
        Element* & matrices with real values & Vuduc, Ahrens, TACO, synthetic \\
        \hline
        Pattern* & matrices with boolean values & SNAP  \\
        \hline 
    \end{tabular}
    \footnotesize *Used in conjunction with aforementioned formats as the innermost level to represent scalar values.
\end{table}

>>>>

\begin{table}[htbp]
    \centering
    \caption{SpMV Tensor Formats}
    \begin{tabular}{|l|l|l|l|}
        \hline
        \textbf{Outer Level} & \textbf{Inner Level} & \textbf{Scalar Values} & \textbf{Style of Matrix}\\
        \hline
        \multirow{7}{*}{Dense} & \multirow{2}{*}{SparseList} & Element & sparse, real-valued matrices \\
        \cline{3-4} 
        & & Pattern & sparse, boolean-valued matrices \\
        \cline{2-4} 
        & \multirow{2}{*}{SparseVBL} & Element & real-valued matrices with blocked structure \\
        \cline{3-4} 
        & & Pattern & boolean-valued matrices with blocked structure \\
        \cline{2-4}
        & \multirow{2}{*}{SparseBand} & Element & real-valued matrices with diagonal band \\
        \cline{3-4} 
        & & Pattern & boolean-valued matrices with diagonal band \\
        \cline{2-4}
        & \multirow{2}{*}{SparsePoint} & Element & real-valued matrices with one value per row \\
        \cline{3-4} 
        & & Pattern & boolean-valued matrices with one value per row \\
        \hline 
    \end{tabular}

\end{table}
